Patterns in Knowledge Production: Political Ruptures and Imperial Dynamics Shaping Public Discourse in Sweden and Finland, 1640–1828

### 2017-10-10 inst/examples/20170201-manuscript.Rmd
stata palette

# Nice theme
theme_set(theme_bw(26))

@@

```{r Fig1, message=FALSE, warning=FALSE, fig.width=10, fig.height=4, echo=FALSE}
library(dplyr)
library(ggplot2)
# theme_set(theme_bw(20))

df <- df0 %>% filter(publication_year >=1640 & publication_year <=1828) %>%
              group_by(catalog, publication_decade) %>%
	      summarise(n = length(unique(na.omit(publication_place))))
p <- ggplot(df, aes(x = publication_decade, y = n, shape = catalog, linetype = catalog)) + 
       geom_point(size = 4) + 
       geom_line(size = 1) + 
       ylab("Places (n)") + xlab("Publication year") +
       scale_color_manual(values = c("blue", "darkgreen")) + 
       guides(shape = guide_legend(title = "Catalog", reverse = TRUE)) +
       guides(linetype = guide_legend(title = "Catalog", reverse = TRUE)) +       
       ggtitle("Unique publication places")
print(p)
```

@@

```{r Fig2, message=FALSE, warning=FALSE, fig.width=10, fig.height=4, echo=FALSE}
library(dplyr)
library(ggplot2)
theme_set(theme_bw(20))
df <- df0 %>% filter(publication_year >=1640 & publication_year <=1828) %>% group_by(catalog, publication_decade) %>% tally()
p <- ggplot(df, aes(x = publication_decade, y = n, shape = catalog, linetype = catalog)) + 
       geom_point(size = 4) + 
       geom_line(size = 1) + 
       ylab("Documents (n)") + xlab("Publication year") +
       scale_color_manual(values = c("blue", "darkgreen")) +
       guides(shape = guide_legend(title = "Catalog", reverse = TRUE)) +
       guides(linetype = guide_legend(title = "Catalog", reverse = TRUE)) +  
       ggtitle("Title count")
print(p)
```

@@

  p <- ggplot(df2, aes(y = paper,
                       x = publication_decade,
  	       shape = gatherings,
		       linetype = gatherings))		       
  p <- p + geom_point(size = 4)
  p <- p + geom_smooth(method = "loess", size = 1,
         aes(color = highlight, fill = highlight))
  p <- p + scale_color_manual(values = c("darkgreen", "darkgray"))
  p <- p + scale_fill_manual(values = c("darkgreen", "darkgray"))  	 
  p <- p + xlab("Year")
  p <- p + ylab("Paper (sheets)")
  p <- p + ylim(c(0, max(na.omit(df2$paper))))
  p <- p + guides(linetype = guide_legend(keywidth = 5, title = "Gatherings"),
       	          shape = guide_legend(keywidth = 5, title = "Gatherings"),
       	          fill = "none", # guide_legend(title = "Gatherings"),
       	          color = "none" # guide_legend(title = "Gatherings")
		  )
  p <- p + ggtitle(paste("Paper consumption (", catal, ")", sep = ""))
  pics[[catal]] <- p
}
```

@@

  theme_set(theme_bw(20))
  p <- ggplot(dff, aes(x = publication_decade, y = f)) +
     geom_bar(position = "stack", stat = "identity", color = "black",
       aes(fill = publication_place)) + 
     xlab("Publication year") +
     #scale_fill_brewer(palette="Spectral")
     scale_fill_brewer(palette="Greys") 
     if (varname == "n") {
       p <- p + ggtitle(paste("Title count (", catalogue, ")", sep = "")) + 
                ylab("Title count frequency (%)") 
     }
     if (varname == "paper") {
       p <- p + ggtitle(paste("Paper (", catalogue, ")", sep = "")) +
                ylab("Paper (%)")        
     }
     if (varname == "publishers") {
       p <- p + ggtitle(paste("Publishers (", catalogue, ")", sep = "")) +
                       ylab("Publishers (%)")
     }     
  p <- p + guides(fill = guide_legend(title = ""))

@@

p <- ggplot(df,
       aes(fill = period, y = paper.per.title, x = publication_place)) + 
       geom_bar(stat = "identity", color = "black", position = "dodge") +
       #scale_x_discrete(labels = c("1757-1765", "1766-1774", "1775-1783")) +
       #scale_fill_manual(values = c("darkgreen", "darkgray"))
       scale_fill_brewer(palette="Greys") +              
       guides(fill = guide_legend(title = "Period")) +
       ylab("Paper (sheets)") + xlab("") +
       ggtitle("Paper consumption per title")

@@

  rectangles$shade <- rep(c("Background", "Highlight"), length = nrow(rectangles))
  riksplace <- c(rep("Unknown", 2), "Stockholm", "Stockholm", "Stockholm", "Norrköping", "Stockholm", rep("Unknown", 3), "Gävle", rep("Unknown", 7))
  #cols <- c("white", "Purple", "yellow", "orange", "darkgray")
  cols <- c("white", "lightgray", "gray", "darkgray")
  rectangles$shade[rectangles$shade == "Highlight"] <- rep(cols, length(which(rectangles$shade == "Highlight")))
  rectangles$shade <- factor(rectangles$shade)

@@

  # Draw Figure
  theme_set(theme_bw(20))
  p <- ggplot() +
         geom_rect(data = rectangles, 
           aes(xmin=xmin, xmax=xmax,
	       ymin=ymin, ymax=ymax,
	       fill=shade), alpha=0.8) +
         #scale_fill_manual(values = cols) +
         scale_fill_brewer(palette="Greys") +
	 guides(fill = "none")

  # p <- p + geom_text(data = rectangles, angle = 90, aes(x=xmin + .5, y=.9*ymax, label=place), size = 6)

@@

theme_set(theme_bw(20))
p <- ggplot(npub, aes(x = publication_decade, y = n)) +
       geom_bar(stat = "identity", position = "stack", color = "black",
       		    aes(fill = publication_place)) + 
       xlab("Publication year") +
       ylab("Unique publishers (n)") +
       scale_fill_brewer(palette="Greys") +       
       guides(fill = guide_legend(reverse = FALSE, title = "")) +
       ggtitle(catal)       
       #ggtitle(paste("Unique publishers in selected publication places (", catalogue, ")"))

@@

p <- ggplot(dfm, aes(x = publication_decade, y = titles_per_capita)) +
       geom_line(aes(linetype = publication_place), size = 1) +
       geom_point(aes(shape = publication_place), size = 5) +
       xlab("Publication decade") +
       ylab("Title count per capita (n)") +
       ggtitle("Title count per capita") +
       guides(shape = guide_legend(title = "Place")) +
       guides(linetype = guide_legend(title = "Place")) 
print(p)

@@

p <- ggplot(df, aes(x = publication_decade, y = n)) +
       geom_line(aes(linetype = publication_place), size = 1) +
       geom_point(aes(shape = publication_place), size = 5) +
       xlab("Publication decade") +
       ylab("Title count (n)") +
       ggtitle("Title count (absolute)") +
       guides(shape = guide_legend(title = "Place")) +
       guides(linetype = guide_legend(title = "Place")) 
print(p)
```

@@

p <- ggplot(df, aes(x = publication_decade, y = paper)) +
       geom_line(aes(linetype = publication_place), size = 1) +
       geom_point(aes(shape = publication_place), size = 5) +
       xlab("Publication year") +
       ylab("Paper (sheets)") +
       ggtitle("Octavo: paper consumption") +
       guides(shape = guide_legend(title = "Place")) +
       guides(linetype = guide_legend(title = "Place"))        
print(p)
```

@@

p <- ggplot(df, aes(x = publication_decade, y = mean_title_length)) +
       geom_bar(aes(fill = publication_place), position = "dodge", stat = "identity") +
       xlab("Publication year") +
       ylab("Title length (words)") +
       ggtitle("Mean title length") +
       scale_fill_manual(values = c("darkgray", "black")) +
       guides(fill = guide_legend(title = "Place", reverse = TRUE))        
print(p)

@@

  for (myplace in myplaces) {
    p <- ggplot(subset(dff, publication_place == myplace),
      aes(x = publication_decade, y = f)) +
      geom_bar(position = "stack", stat = "identity",
      			aes(fill = language), color = "black") + 
      xlab("Publication year") +
      ylab("Title count frequency (%)") +
      ggtitle(paste(myplace, "/", catalogue)) +
      #scale_fill_brewer(palette="Spectral") +
      scale_fill_brewer(palette="Greys") +       
      guides(fill = guide_legend(title = "")) 
      #guides(fill = guide_legend(title = "")) +       
    pics[[paste(catalogue, myplace, sep = "-")]] <- p
  }
}

@@

p <- ggplot(df, aes(x = publication_year, y = n, shape = language)) +
       geom_line(size = 1, aes(linetype = language)) +
       geom_point(size = 4) +
       scale_color_brewer(palette="Greys") +
       scale_fill_brewer(palette="Greys") +                     
       geom_smooth(color = "black") +
       guides(shape = guide_legend(title = "Language")) +
       guides(linetype = guide_legend(title = "Language")) + 
       ylab("Title count (n)") +
       xlab("Publication year")

@@

  # PAPER CONSUMPTION
  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
       geom_point(aes(shape = language), size = 5) +
       geom_line(aes(linetype = language), size = 1) +       
       xlab("Publication year") +
       ylab("Paper (sheets)") +
       guides(shape = guide_legend(title = "Language")) +
       guides(linetype = guide_legend(title = "Language")) + 
       #ggtitle(paste("Temporary Sermons (", catalogue, ")", sep = ""))
       ggtitle(catalogue)       
  print(p)
```

@@

# PAPER CONSUMPTION
theme_set(theme_bw(20))
p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
       geom_point(aes(shape = language), size = 5) +
       geom_line(aes(linetype = language)) +       
       xlab("Publication year") +
       ylab("Paper (sheets)") +
       guides(shape = guide_legend(title = "Language")) +
       guides(linetype = guide_legend(title = "Language")) +        
       ggtitle(catalogue)
       #ggtitle(paste("Devotional Literature (", catalogue, ")", sep = "")) 
print(p)
```

>>>>

# Nice theme
# theme_set(theme_bw(26))

@@

```{r Fig1, message=FALSE, warning=FALSE, fig.width=10, fig.height=4, echo=FALSE}
library(dplyr)
library(ggplot2)
library(ggthemes)
# theme_set(theme_bw(20))
theme_set(theme_minimal(20))

df <- df0 %>% filter(publication_year >=1640 & publication_year <=1828) %>%
              group_by(catalog, publication_decade) %>%
	      summarise(n = length(unique(na.omit(publication_place))))
p <- ggplot(df, aes(x = publication_decade, y = n,
       color = catalog, shape = catalog)) + 
       geom_point(size = 4) + 
       geom_line(size = 1) + 
       ylab("Places (n)") + xlab("Publication year") +
       # scale_color_manual(values = c("blue", "darkgreen")) + 
       guides(linetype = "none") +
       guides(shape = guide_legend(title = "Catalog", reverse = TRUE),
              color = guide_legend(title = "Catalog", reverse = TRUE)) +              
       ggtitle("Unique publication places") +
       scale_color_stata()
print(p)
```

@@

```{r Fig2, message=FALSE, warning=FALSE, fig.width=10, fig.height=4, echo=FALSE}
library(dplyr)
library(ggplot2)
theme_set(theme_bw(20))
df <- df0 %>% filter(publication_year >=1640 & publication_year <=1828) %>%
        group_by(catalog, publication_decade) %>% tally()
p <- ggplot(df, aes(x = publication_decade, y = n,
                    shape = catalog,
		    color = catalog)) + 
       geom_point(size = 4) + 
       geom_line(size = 1) + 
       ylab("Documents (n)") + xlab("Publication year") +
       #scale_color_manual(values = c("blue", "darkgreen")) +
       guides(
         shape = guide_legend(title = "Catalog", reverse = TRUE),
         color = guide_legend(title = "Catalog", reverse = TRUE)	 
       ) +
       ggtitle("Title count") +
       scale_color_stata()
print(p)
```

@@

  p <- ggplot(df2, aes(y = paper,
                       x = publication_decade,
  	       shape = gatherings,
		       color = gatherings))		       
  p <- p + geom_point(size = 4)
  p <- p + geom_smooth(method = "loess", size = 1,
         aes(color = highlight, fill = highlight))
  #p <- p + scale_color_manual(values = c("darkgreen", "darkgray"))
  #p <- p + scale_fill_manual(values = c("darkgreen", "darkgray"))  	 
  p <- p + xlab("Year")
  p <- p + ylab("Paper (sheets)")
  p <- p + ylim(c(0, max(na.omit(df2$paper))))

  p <- p + ggtitle(paste("Paper consumption (", catal, ")", sep = "")) +
         scale_color_stata() +
         scale_fill_stata() + 
         guides(
       	          shape = guide_legend(keywidth = 5, title = "Gatherings"),
       	          fill = "none", # guide_legend(title = "Gatherings"),
       	          color = "none" # guide_legend(title = "Gatherings")
		  )

  pics[[catal]] <- p
}
```

@@

  theme_set(theme_bw(20))
  p <- ggplot(dff, aes(x = publication_decade, y = f)) +
     geom_bar(position = "stack", stat = "identity", color = "black",
       aes(fill = publication_place)) + 
     xlab("Publication year") +
     scale_fill_stata() 
     #scale_fill_brewer(palette="Spectral")     
     #scale_fill_brewer(palette="Greys") 
     if (varname == "n") {
       p <- p + ggtitle(paste("Title count (", catalogue, ")", sep = "")) + 
                ylab("Title count frequency (%)") 
     }
     if (varname == "paper") {
       p <- p + ggtitle(paste("Paper (", catalogue, ")", sep = "")) +
                ylab("Paper (%)")        
     }
     if (varname == "publishers") {
       p <- p + ggtitle(paste("Publishers (", catalogue, ")", sep = "")) +
                       ylab("Publishers (%)")
     }     
  p <- p + guides(fill = guide_legend(title = ""))

@@

p <- ggplot(df,
       aes(fill = period, y = paper.per.title, x = publication_place)) + 
       geom_bar(stat = "identity", color = "black", position = "dodge") +
       #scale_x_discrete(labels = c("1757-1765", "1766-1774", "1775-1783")) +
       #scale_fill_manual(values = c("darkgreen", "darkgray"))
       #scale_fill_brewer(palette="Greys") +
       scale_fill_stata() +       
       guides(fill = guide_legend(title = "Period")) +
       ylab("Paper (sheets)") + xlab("") +
       ggtitle("Paper consumption per title")

@@

  rectangles$shade <- rep(c("Background", "Highlight"), length = nrow(rectangles))
  riksplace <- c(rep("Unknown", 2), "Stockholm", "Stockholm", "Stockholm", "Norrköping", "Stockholm", rep("Unknown", 3), "Gävle", rep("Unknown", 7))
  cols <- c("white", "Purple", "yellow", "orange", "darkgray")
  #cols <- c("white", "lightgray", "gray", "darkgray")
  rectangles$shade[rectangles$shade == "Highlight"] <- rep(cols, length(which(rectangles$shade == "Highlight")))
  rectangles$shade <- factor(rectangles$shade)

@@

  # Draw Figure
  theme_set(theme_bw(20))
  p <- ggplot() +
         geom_rect(data = rectangles, 
           aes(xmin=xmin, xmax=xmax,
	       ymin=ymin, ymax=ymax,
	       fill=shade), alpha=0.8) +
	 scale_fill_stata() +
         #scale_fill_manual(values = cols) +
         #scale_fill_brewer(palette="Greys") +
	 guides(fill = "none")

@@

theme_set(theme_bw(20))
p <- ggplot(npub, aes(x = publication_decade, y = n)) +
       geom_bar(stat = "identity", position = "stack", color = "black",
       		    aes(fill = publication_place)) + 
       xlab("Publication year") +
       ylab("Unique publishers (n)") +
       scale_fill_stata() +       
       guides(fill = guide_legend(reverse = FALSE, title = "")) +
       ggtitle(catal)

@@

p <- ggplot(dfm, aes(x = publication_decade, y = titles_per_capita)) +
       geom_line(aes(color = publication_place), size = 1) +
       geom_point(aes(shape = publication_place, color = publication_place), size = 5) +
       xlab("Publication decade") +
       ylab("Title count per capita (n)") +
       scale_color_stata() +
       ggtitle("Title count per capita") +
       guides(shape = guide_legend(title = "Place")) +
       guides(color = guide_legend(title = "Place")) 
print(p)

@@

p <- ggplot(df, aes(x = publication_decade, y = n)) +
       geom_line(aes(color = publication_place), size = 1) +
       geom_point(aes(shape = publication_place), size = 5) +
       xlab("Publication decade") +
       ylab("Title count (n)") +
       ggtitle("Title count (absolute)") +
       guides(shape = guide_legend(title = "Place")) +
       guides(color = guide_legend(title = "Place")) +
       scale_color_stata()
print(p)
```

@@

p <- ggplot(df, aes(x = publication_decade, y = paper)) +
       geom_line(aes(color = publication_place), size = 1) +
       geom_point(aes(shape = publication_place), size = 5) +
       xlab("Publication year") +
       ylab("Paper (sheets)") +
       ggtitle("Octavo: paper consumption") +
       guides(shape = guide_legend(title = "Place"), color = guide_legend(title = "Place")) +
       scale_color_stata()
print(p)
```

@@

p <- ggplot(df, aes(x = publication_decade, y = mean_title_length)) +
       geom_bar(aes(fill = publication_place), position = "dodge", stat = "identity") +
       xlab("Publication year") +
       ylab("Title length (words)") +
       ggtitle("Mean title length") +
       scale_fill_stata() +
       guides(fill = guide_legend(title = "Place", reverse = TRUE))        
print(p)
```

@@

  for (myplace in myplaces) {
    p <- ggplot(subset(dff, publication_place == myplace),
      aes(x = publication_decade, y = f)) +
      geom_bar(position = "stack", stat = "identity",
      			aes(fill = language), color = "black") + 
      xlab("Publication year") +
      ylab("Title count frequency (%)") +
      ggtitle(paste(myplace, "/", catalogue)) +
      scale_fill_stata() +
      #scale_fill_brewer(palette="Greys") +       
      guides(fill = guide_legend(title = "")) 
      #guides(fill = guide_legend(title = "")) +       
    pics[[paste(catalogue, myplace, sep = "-")]] <- p
  }
}

@@

p <- ggplot(df, aes(x = publication_year, y = n, shape = language)) +
       geom_line(size = 1, aes(color = language)) +
       geom_point(size = 4) +
       scale_color_brewer(palette="Greys") +
       scale_fill_brewer(palette="Greys") +                     
       geom_smooth(color = "black") +
       guides(shape = guide_legend(title = "Language"),
              color = guide_legend(title = "Language")) +
       scale_color_stata() +
       ylab("Title count (n)") +
       xlab("Publication year")

@@

  # PAPER CONSUMPTION
  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
       geom_point(aes(shape = language), size = 5) +
       geom_line(aes(color = language), size = 1) +       
       xlab("Publication year") +
       ylab("Paper (sheets)") +
       guides(shape = guide_legend(title = "Language"), color = guide_legend(title = "Language")) +
       scale_color_stata() +
       ggtitle(catalogue)       
  print(p)
```

@@

# PAPER CONSUMPTION
theme_set(theme_bw(20))
p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
       geom_point(aes(shape = language), size = 5) +
       geom_line(aes(color = language)) +       
       xlab("Publication year") +
       ylab("Paper (sheets)") +
       guides(shape = guide_legend(title = "Language"), color = guide_legend(title = "Language")) +
       scale_color_stata() +
       ggtitle(catalogue)
